Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-15 paper/paper.tex
Section intro

	The best known deterministic algorithm is $O(k^2\cdot \ell^2)$-competitive \cite{?????},
	and the best known lower bound for the competitive ratio of
	deterministic algorithms is $\Omega(k)$,
	which uses a reduction from the online paging problem.
	  In this paper, we provide the lower bound of $\Omega(k\cdot \ell)$.
    We also present an optimal algorithm for the case of $k=3$.
  Finally,
  we provide a $O(k\cdot \ell)$-competitive algorithm for the variant
  where the optimal configuration is always a fixed partition
  that incurs zero communication cost through the whole request sequence.
\end{abstract}

@@

@@

@@

  In this section we provide an optimal algorithm for the case $k=3$.

>>>>

	The best known deterministic algorithm is $O(k^2\cdot \ell^2)$-competitive \cite{?????} \maciek{We should cite \cite{repartition-disc} here.},
	and the best known lower bound for the competitive ratio of
	deterministic algorithms is $\Omega(k)$,
	which uses a reduction from the online paging problem.
	  In this paper, we provide the lower bound of $\Omega(k\cdot \ell)$.
    We also present an optimal algorithm for the case of $k=3$.
  Finally,
  we provide a $O(k\cdot \ell)$-competitive algorithm for the variant
  where the optimal configuration is always a fixed partition
  that incurs zero communication cost through the whole request sequence.
\end{abstract}

@@

\maciek{emphasize that lower bound works for $k=3$ already. Also in the proof?}

@@

\todo{Make sure our manuscript is autor anonymous}

@@

  In this section we show that the classic \emph{rent-or-buy} approach yields an optimal algorithm for $k=3$.
  Upon receiving $\alpha$ requests between a pair of nodes, we collocate them in one server until the end of an epoch (that we define precisely later).
  To this end, we maintain \emph{components of nodes}, in similar way to \cite{repartition-disc}.
